The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
reflow
rm write.bibtex from Rmd
rm italics seasons

### Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on social (visual and auditory perception), spatial (habitat
type), and temporal (seasonal). Caribou are gregarious ungulates with
fission-fusion dynamics (Lesmerises et al. 2018) that display temporal
[@Peignier_2019] and spatial (Webber et al. unpublished data) variation in
social networks. In winter, caribou dig holes in the snow, termed craters, to
access forage (Bergerud 1974). As a result, caribou tend to occupy and re-use
craters once they are established and there is considerably less access to
forage than when the landscape is snow-free. Importantly, craters exist on the
landscape at multiple scales: the crater scale (a single crater), the feeding
area scale (multiple craters in close proximity), and the winter range scale
(all craters within an individual’s range) [@Mayor_2009]. The distribution of
forage for caribou is therefore seasonally heterogeneous, with greater access in
snow-free seasons compared to winter as well as spatially heterogeneous in
winter because the distribution of craters on the landscape varies meaning that
access to vegetation in winter is highly variable for caribou. We therefore
partitioned data into two discrete seasons:  *summer (3 August - 20 September)
and winter (1 January – 17 February)* based on caribou socioecology
[@Peignier_2019].

@@

```{r, message=FALSE}
write.bibtex(file = "../references/knitcite.bib")
```

>>>>

### Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on social (visual and auditory perception), spatial (habitat
type), and temporal (seasonal). Caribou are gregarious ungulates with
fission-fusion dynamics (Lesmerises et al. 2018) that display temporal
[@Peignier_2019] and spatial (Webber et al. unpublished data) variation in
social networks. In winter, caribou dig holes in the snow, termed craters, to
access forage (Bergerud 1974). As a result, caribou tend to occupy and re-use
craters once they are established and there is considerably less access to
forage than when the landscape is snow-free. Importantly, craters exist on the
landscape at multiple scales: the crater scale (a single crater), the feeding
area scale (multiple craters in close proximity), and the winter range scale
(all craters within an individual’s range) [@Mayor_2009]. The distribution of
forage for caribou is therefore seasonally heterogeneous, with greater access in
snow-free seasons compared to winter as well as spatially heterogeneous in
winter because the distribution of craters on the landscape varies meaning that
access to vegetation in winter is highly variable for caribou. We therefore
partitioned data into two discrete seasons:  summer (3 August - 20 September)
and winter (1 January – 17 February) based on caribou socioecology
[@Peignier_2019].

@@
